SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-06-19 scipy-1.0/paper.tex
Grammar and typos

SciPy provides fundamental algorithms for scientific computing. The
breadth of its scope was derived from the Guide to Available Mathematical
Software classification system (GAMS\cite{boisvert1991guide}). In areas
that move relatively slowly, e.g. linear algebra, SciPy aims to provide
complete coverage. In other areas it aims to provide fundamental building
blocks while interacting well with other packages specialized in that area.
For example, SciPy provides what one expects to find in a
statistics textbook (probability distributions, hypothesis tests, frequency
statistics, correlation functions, and more), while 
Statsmodels\cite{statsmodels2010} provides
more advanced statistical estimators and inference methods;
scikit-learn\cite{pedregosa2011scikit} covers machine learning; and
PyMC3\cite{10.7717/peerj-cs.55}, emcee\cite{2013PASP-emcee} and 
PyStan\cite{pystan-ref} cover Bayesian statistics and probabilistic modeling.
scikit-image\cite{vanderwalt2014scikit} provides image processing
capabilities beyond \texttt{scipy.ndimage}, sympy\cite{meurer2017sympy}
provides a Python interface for symbolic computation, and
NetworkX\cite{hagberg2008networkx} is a Python library for probing
graphs and networks in a more specialized way than SciPy components
like \texttt{sparse.csgraph} or \texttt{spatial}.

@@

In terms of software systems and architecture, SciPy's scope matches NumPy's:
algorithms for in-memory computing on single machines, with support for a wide
range of data types and process architectures. Distributed computing and support
for graphics processing units (GPUs) is explicitly out of scope.

>>>>

SciPy provides fundamental algorithms for scientific computing. The
breadth of its scope was derived from the Guide to Available Mathematical
Software classification system (GAMS\cite{boisvert1991guide}). In areas
that move relatively slowly, e.g. linear algebra, SciPy aims to provide
complete coverage. In other areas it aims to provide fundamental building
blocks while interacting well with other packages specialized in that area.
For example, SciPy provides what one expects to find in a
statistics textbook (probability distributions, hypothesis tests, frequency
statistics, correlation functions, and more), while 
Statsmodels\cite{statsmodels2010} provides
more advanced statistical estimators and inference methods;
scikit-learn\cite{pedregosa2011scikit} covers machine learning; and
PyMC3\cite{10.7717/peerj-cs.55}, emcee\cite{2013PASP-emcee} and 
PyStan\cite{pystan-ref} cover Bayesian statistics and probabilistic modeling.
scikit-image\cite{vanderwalt2014scikit} provides image processing
capabilities beyond SciPy's \texttt{ndimage}, sympy\cite{meurer2017sympy}
provides a Python interface for symbolic computation, and
NetworkX\cite{hagberg2008networkx} is a Python library for probing
graphs and networks in a more specialized way than SciPy components
like \texttt{sparse.csgraph} or \texttt{spatial} offer.

@@

In terms of software systems and architecture, SciPy's scope matches NumPy's:
algorithms for in-memory computing on single machines, with support for a wide
range of data types and process architectures. Distributed computing and support
for graphics processing units (GPUs) are explicitly out of scope.
